ChIP-seq example

### 2018-10-19 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

```{r load-pkgs, warning=FALSE}
source("../code/chipseq.functions.R")
library(smashr)
library(ggplot2)
library(cowplot)
```

@@

TO DO: Describe what is being shown in the plot.

@@

>>>>

```{r load-pkgs, warning=FALSE, message=FALSE}
source("../code/chipseq.functions.R")
library(smashr)
library(ggplot2)
library(cowplot)
```

@@

This next plot shows the intensity function estimated by SMASH (orange
line). The read count data are depicted as light blue circles, in
which the area of each circle is scaled by the number of data points
that fall within each 1.6-kb "bin". (We show counts summarized within
bins because there are too many data points to plot them
individually.)

The peaks identified by the MACS software are shown as red
triangles. (Specifically, these are the *mean positions* of the
identified peak intervals; the peak intervals are short enough that it
is not useful to show both the start and end positions of these
intervals.)

@@

Based on this plot, it is clear that the the strongest SMASH intensity
estimates align very closely with the peaks found by MACS.

Intriguingly, the SMASH estimates also suggest the presence of several
additional weaker peaks that were not identified by MACS.
